Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-01-28 paper/paper.tex
finding some room for new contributions

%\begin{wraptable}[10]{r}{0.25\textwidth}
%  \vspace{-3ex}
%\end{wraptable}

We used the official conformance test suite
Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
engines to the \js\ current standard. As it is acceptable to release
engines fulfilling the specification only partially~\cite{kangax}, it
is expected that engines do not fully pass this test. However, we
expect that results provide indication of engine's maturity. In the
limit, it is not desirable to flood bug reports on engines at early
stages of development. We ran the suite once a day for seven
\begin{wraptable}[12]{r}{0.2\textwidth}  
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  \small
  \begin{tabular}{crr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc{} & 92\%\\
    \veight{} & 95\% \\
    \chakra{} & 75\% \\    
    \smonkey{} & 93\% \\
    \bottomrule
  \end{tabular}
  \normalsize
\end{wraptable}
consecutive days from the period of 16 to 22 of August,
2018. Table~\ref{tab:test262} shows the average number of passing
tests over this period. The variance of results was negligible; for
that reasons, we omitted standard deviations. We noticed that all four
engines we analyzed but \chakra{} use some variant of the Test262
suite as part of their regression process, but we used the same
version in this experiment; the one available from the Test262 web
site~\cite{ecma262-conformance-suite}. Results show that there are
still many unsupported cases as can be observed from the percentages
in the table, but the number of passing tests is high, with
\veight\ and \smonkey\ performing better compared to others and
\chakra\ performing well worse than others. It is important to
highlight that failures in this conformance test suite indicates
missing features as opposed to bugs. However, note that \chakra\ is
both the engine that has the lowest passing ratio in the conformance
test suite and the one we were able to find more bugs. Although it is
possible to find correlation between the percentage of passing tests
in the conformance suite (as per Table~\ref{tab:test262}) and reliability as
measured by the number of bugs found (as per
Figure~\ref{fig:summary}), we do not not imply causality.

@@

\vspace{0.5ex}
\subsubsection{Methodology}
\label{sec:methodology}
In this experiment, a developer with experience in \js\ analyzed each
test file that reveals failure in a given engine and classified that
file as potentially fault-revealing or not. The co-authors supervised
the classification process to validate correctness. For the cases the
developer classified the failures as potentially fault-revealing, one
of the co-authors carefully inspected the case and reported the bug,
if confirmed, or re-classified the failure as a false alarm.

\vspace{0.5ex}
\subsubsection{Results}
\label{sec:results}

@@

%% This suggests that the investiment in
%% testing paid off in this case.
\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0 
      JSC 2 
      Spidermonkey 58
    }
    \jsc{} & - & 9 & 10 & 58   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 218 & 107 & - & 279 \\
    Duktape & 0 & 4 & 4 & 1   \\
    \jerry{} & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\ 
   Tiny-js & 0 & 0 & 0 & 0  \\
    \midrule
   \textbf{total} & 270 & 145 & 36 & 361 \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

%% \begin{figure}[h]
%%   \centering
%%   \subfloat[\label{fig:falsepositives}False Positives]{%
%%     \includegraphics[trim=0 150 0 100,clip,width=0.4\textwidth]{R/piecharts/falsepositives}
%%   }
%%   \label{1a}\hfill
%%   \subfloat[\label{fig:truepositives}True Positives]{%
%%     \includegraphics[trim=0 150 0 150,clip,width=0.4\textwidth]{R/piecharts/truepositives}    
%%   }
%%   \label{1b}\\
%%   \caption{\label{fig:piecharts-transplantation}False and True positives.}
%% \end{figure}

\begin{table}[t!]
  \small
%  \setlength{\tabcolsep}{4pt}    
  \centering
  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution of false and true positives.}
  \begin{tabular}{ccr}
    \toprule
    & source &  \#\\
    \midrule
    \multirow{5}{*}{False Positives} & Undefined Behavior & 252 \\
    & Timeout/OME & 15 \\
    & Not Implemented & 22 \\
    & Non-Standard Element & 119 \\
    & Other & 135 \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & 10 \\
    & Bug & 24 \\
    \bottomrule
  \end{tabular}
\end{table}

%%  The piechart at the top
%% shows false alarms. The absolute number of tests in each category is
%% shown in parentheses to the right-side of each slice label naming the
%% source of false positive.

@@

% (\eg{},``New'', ``Rejected'', ``Confirmed'', ``Fixed'')

Table~\ref{fig:piecharts-transplantation} shows the distribution of
false and true positives. Considering false positives, ``Undefined
Behavior'' was the most predominant source. Considering true
positives, we found a reasonable number of duplicate reports, but not
enough high to justify attempting to automate the detection of
duplicates.  Table~\ref{tab:test-transplantation-bugs} lists all bugs
we found with test transplantation. The first column shows the
identifier we assigned to the bug\Comment{, column ``Date'' shows the
  date the bug was reported in the format ``m/dd'',}, column
``Engine'' shows the affected engine, column ``Status'' shows the
status of the bug report at the time of the writing. The status string
appears in bold face for status ``Confirmed'' or higher, \ie{},
``Assigned'' and ``Fixed''.  Column ``Url'' shows the URL
(de-anonymized upon request) for the bug report entry in the
corresponding bug-tracking system, column ``Severity'' shows the
severity level for confirmed bugs, and, finally, column ``Suite''
shows the name of the engine that originated the test.

%Note that bug reports \#4 and \#23 afected multiple engines.

@@

@@

Table~\ref{tab:summary-hi} shows statistics of \hi\ warnings; recall
from Section~\ref{sec:clusterization} that we do not cluster
\hi\ warnings\Comment{ as there was no clear clustering criteria to
  use for that}. This table breaks down \hi\ warning by the affected
engine, \ie, the engine manifesting distinct output among those
analyzed. Column ``+1'' shows the cases where more than one engine
disagree on the output. Note from the totals that the ordering of
engines is consistent with the one observed on
Table~\ref{tab:cross-testing}, with \chakra\ and \jsc\ holding first
and second place, respectively, in number of warnings (/failures)
compared to other engines.

>>>>

\begin{wraptable}[11]{r}{0.22\textwidth}
  \vspace{-4ex}      
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  \small
  \begin{tabular}{crr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc{} & 92\%\\
    \veight{} & 95\% \\
    \chakra{} & 75\% \\    
    \smonkey{} & 93\% \\
    \bottomrule
  \end{tabular}
  \normalsize
  \vspace{-4ex}
\end{wraptable}
We used the official conformance test suite
Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
engines to the \js\ current standard. As it is acceptable to release
engines fulfilling the specification only partially~\cite{kangax}, it
is expected that engines do not fully pass this test. However, we
expect that results provide indication of engine's maturity. In the
limit, it is not desirable to flood bug reports on engines at early
stages of development. We ran the suite once a day for seven
consecutive days from the period of 16 to 22 of August,
2018. Table~\ref{tab:test262} shows the average number of passing
tests over this period. The variance of results was negligible; for
that reasons, we omitted standard deviations. We noticed that all four
engines we analyzed but \chakra{} use some variant of the Test262
suite as part of their regression process, but we used the same
version in this experiment; the one available from the Test262 web
site~\cite{ecma262-conformance-suite}. Results show that there are
still many unsupported cases as can be observed from the percentages
in the table, but the number of passing tests is high, with
\veight\ and \smonkey\ performing better compared to others and
\chakra\ performing well worse than others. It is important to
highlight that failures in this conformance test suite indicates
missing features as opposed to bugs. However, note that \chakra\ is
both the engine that has the lowest passing ratio in the conformance
test suite and the one we were able to find more bugs. Although it is
possible to find correlation between the percentage of passing tests
in the conformance suite (as per Table~\ref{tab:test262}) and reliability as
measured by the number of bugs found (as per
Figure~\ref{fig:summary}), we do not not imply causality.

@@

%\vspace{0.5ex}
\subsubsection{Methodology}
\label{sec:methodology}
In this experiment, a developer with experience in \js\ analyzed each
test file that reveals failure in a given engine and classified that
file as potentially fault-revealing or not. The co-authors supervised
the classification process to validate correctness. For the cases the
developer classified the failures as potentially fault-revealing, one
of the co-authors carefully inspected the case and reported the bug,
if confirmed, or re-classified the failure as a false alarm.

%\vspace{0.5ex}
\subsubsection{Results}
\label{sec:results}

@@

%% This suggests that the investiment in
%% testing paid off in this case.
\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
    test suites.}
  \renewcommand*{\arraystretch}{0.9}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0 
      JSC 2 
      Spidermonkey 58
    }
    \jsc{} & - & 9 & 10 & 58   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 218 & 107 & - & 279 \\
    Duktape & 0 & 4 & 4 & 1   \\
    \jerry{} & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\ 
   Tiny-js & 0 & 0 & 0 & 0  \\
    \midrule
   \textbf{total} & 270 & 145 & 36 & 361 \\
    \bottomrule 
  \end{tabular}
  \vspace{-3ex}
\end{table}

@@

\begin{wraptable}[12]{r}{0.23\textwidth}  
  \small
  \centering
  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution
    of False (FP) and True Positives (TP).}
  \setlength{\tabcolsep}{3pt}      
  \renewcommand*{\arraystretch}{0.9}
  \begin{tabular}{ccr}
    \toprule
    & source &  \#\\
    \midrule
    \multirow{5}{*}{FP} & Undefined Behavior & 252 \\
    & Timeout/OME & 15 \\
    & Not Implemented & 22 \\
    & Non-Standard Element & 119 \\
    & Other & 135 \\
    \midrule
    \multirow{2}{*}{TP} & Duplicate & 10 \\
    & Bug & 24 \\
    \bottomrule
  \end{tabular}
\end{wraptable}
Table~\ref{fig:piecharts-transplantation} shows the distribution of
false and true positives. Considering false positives, ``Undefined
Behavior'' was the most predominant source. Considering true
positives, we found a reasonable number of duplicate reports, but not
enough high to justify attempting to automate the detection of
duplicates.  Table~\ref{tab:test-transplantation-bugs} lists all bugs
we found with test transplantation. The first column shows the
identifier we assigned to the bug\Comment{, column ``Date'' shows the
  date the bug was reported in the format ``m/dd'',}, column
``Engine'' shows the affected engine, column ``Status'' shows the
status of the bug report at the time of the writing. The status string
appears in bold face for status ``Confirmed'' or higher, \ie{},
``Assigned'' and ``Fixed''.  Column ``Severity'' shows the
severity of confirmed bugs, and, finally, column ``Suite''
shows the name of the engine that originated the test.

%% ``Url'' shows the URL
%% (de-anonymized upon request) for the bug report entry in the
%% corresponding bug-tracking system, column

@@

@@

Table~\ref{tab:summary-hi} shows statistics of \hi\ warnings, which
are not clustered. The table breaks down \hi\ warning by the affected
engine, \ie, the engine manifesting distinct output among those
analyzed. Column ``+1'' shows the cases where more than one engine
disagree on the output. Note from the totals that the ordering of
engines is consistent with the one observed on
Table~\ref{tab:cross-testing}, with \chakra\ and \jsc\ in first and
second places, respectively, in number of warnings.

@@

### 2019-01-28 paper/table_differential.tex
adding extra space to fill 10 pages
formatting paper to ISSTA + adding important comments to paper
updated ACM style
finding some room for new contributions

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of cross-engine
    differential testing.}
  \label{tab:bugs}
  \begin{tabular}{ccccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  &
    \multicolumn{1}{c}{Url}  & Severity & Priority & Suite \\
    \midrule
%    \multicolumn{9}{c}{\emph{Exploratory Phase}} \\
%    \midrule    
    1  & 4/12 & radamsa & \chakra{}   & \textbf{Fixed}  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}
    & 2 & \textbf{\lo} & \jsc{} \\ 
    2  & 4/12 & radamsa & \chakra{}   & Rejected  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}
    & - & \hi{} & \jsc{} \\
    3  & 4/14 & radamsa & \jsc{}  & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
    } & -  & \hi{} & \jsc{}    \\
    4  & 4/25 & radamsa & \chakra{}  & \textbf{Fixed}     &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}
    & 2 & \hi{} & \jerry{}   \\
    5  & 4/29 & radamsa & \jsc{}  & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
    } & 2  & \hi{}  & \jerry{}\\

    \midrule
    \multirow{2}{*}{6} & \multirow{2}{*}{4/30}  &
    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5076}{\#5076}}
    & 2 & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{TinyJS}\\    
                        &                        &        &
    \jsc{} & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
    & - &  & \\
    \midrule

    7 & 5/02 & radamsa & \jsc{}  & \textbf{Fixed} &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
    & 2 & \textbf{\lo} & \smonkey{} \\
    8 & 5/10 & radamsa & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5128}{\#5128}}
    & 3 & \hi{} & \jerry{} \\
    9 & 5/17 & radamsa & \chakra{} & \textbf{Fixed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5182}{\#5182}}
    & 2 & \hi{} & \veight{}\\
    10 & 5/24 & radamsa & \jsc{} & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
    & 2 & \hi{} & \jsc{}\\
    11 & 6/26 & radamsa & \jsc{} & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
    & 2 & \hi{} & \jerry{}\\
    12 & 7/10 & quickfuzz & \jsc{} & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
    & 2 & \hi{} & \jerry{}\\
    13 & 7/10 & quickfuzz & \chakra{} & \textbf{Confirmed}  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5443}{\#5443}}
    & 2 & \hi{} & \jerry{}\\
    %    \multicolumn{9}{c}{\emph{Non-Exploratory Phase}} \\

    \midrule
    \multirow{2}{*}{14} & \multirow{2}{*}{8/21}  &
    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}
    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
    & & &
    \veight{} & \textbf{Fixed} &
    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}
    & 2 &  & \\
    \midrule

    15 & 8/23 & quickfuzz & \jsc{} & New  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188899}{\#188899}}
    & - & \hi{} & Test262\\
    16 & 8/23 & quickfuzz & \veight{} & \textbf{Confirmed}  &
    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8088}{\#8088}}
    & 2 & \hi{} & Test262\\

    \midrule
    \multirow{2}{*}{17} & \multirow{2}{*}{8/24}  &
    \multirow{2}{*}{quickfuzz} & \chakra{} & New &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5630}{\#5630}}
    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
    & & & 
    \jsc{} & New &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188920}{\#188920}}
    & - &  & \\
   \bottomrule
  \end{tabular}
\end{table*}

>>>>

\begin{table}[t]
  \small
  \vspace{-3ex}
  \centering
  \caption{List of bug reports issued as result of cross-engine
    differential testing.}
  \label{tab:bugs}
  \setlength{\tabcolsep}{2pt}
  \renewcommand{\arraystretch}{0.95}
  \begin{tabular}{rcccccc}
    \toprule
    Issue\# \Comment{ & Date} & Fuzzer & Engine  & Status \Comment{&
    \multicolumn{1}{c}{Url}}  & Severity & Priority & Suite \\
    \midrule
    1  \Comment{& 4/12} & radamsa & \chakra{}   & \textbf{Fixed}  \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}}
    & 2 & \textbf{\lo} & \jsc{} \\ 
    2  \Comment{& 4/12} & radamsa & \chakra{}   & WontFix  \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}}
    & - & \hi{} & \jsc{} \\
    3  \Comment{& 4/14} & radamsa & \jsc{}  & New \Comment{&
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}}
    } & -  & \hi{} & \jsc{}    \\
    4  \Comment{& 4/25} & radamsa & \chakra{}  & \textbf{Fixed}     \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}}
    & 2 & \hi{} & \jerry{}   \\
    5  \Comment{& 4/29} & radamsa & \jsc{}  & \textbf{Fixed}  \Comment{&
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}}
    } & 2  & \hi{}  & \jerry{}\\

    6 \Comment{& 4/30}  & radamsa & \chakra{} & \textbf{Confirmed} \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5076}{\#5076}}}
    & 2 & \hi{} & TinyJS\\

    7                    \Comment{& 4/30}                       &  radamsa   &
    \jsc{} & New \Comment{&
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}}
    & - & \hi{} & TinyJS \\

    8 \Comment{& 5/02} & radamsa & \jsc{}  & \textbf{Fixed} \Comment{&
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}}
    & 2 & \textbf{\lo} & \smonkey{} \\
    9 \Comment{& 5/10} & radamsa & \chakra{} & \textbf{Confirmed} \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5128}{\#5128}}}
    & 3 & \hi{} & \jerry{} \\
    10 \Comment{& 5/17} & radamsa & \chakra{} & \textbf{Fixed} \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5182}{\#5182}}}
    & 2 & \hi{} & \veight{}\\
    11 \Comment{& 5/24} & radamsa & \jsc{} & \textbf{Fixed}  \Comment{&
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}}
    & 2 & \hi{} & \jsc{}\\
    12 \Comment{& 6/26} & radamsa & \jsc{} & \textbf{Fixed}  \Comment{&
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}}
    & 2 & \hi{} & \jerry{}\\
    13 \Comment{& 7/10} & quickfuzz & \jsc{} & \textbf{Fixed}  \Comment{&
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}}
    & 2 & \hi{} & \jerry{}\\
    14 \Comment{& 7/10} & quickfuzz & \chakra{} & \textbf{Confirmed}  \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5443}{\#5443}}}
    & 2 & \hi{} & \jerry{}\\
    %    \multicolumn{9}{c}{\emph{Non-Exploratory Phase}} \\

    15 \Comment{& 8/21}  & radamsa & \chakra{} & \textbf{Confirmed} \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}}
    & - & \hi{} & Test262\\

    16 \Comment{& 8/21} & radamsa &
    \veight{} & \textbf{Fixed} \Comment{&
    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}}
    & 2 & \hi{} & Test262 \\

    17 \Comment{& 8/23} & quickfuzz & \jsc{} & New  \Comment{&
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188899}{\#188899}}}
    & - & \hi{} & Test262\\
    18 \Comment{& 8/23} & quickfuzz & \veight{} & \textbf{Confirmed}  \Comment{&
    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8088}{\#8088}}}
    & 2 & \hi{} & Test262\\

    19 \Comment{& 8/24}  & quickfuzz & \chakra{} & New \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5630}{\#5630}}}
    & - & \hi{} & Test262\\

    20 \Comment{& 8/24} &  quickfuzz & 
    \jsc{} & New \Comment{&
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188920}{\#188920}}}
    & - & \hi{} & Test262 \\

    21 \Comment{& 8/24} & quickfuzz & \jsc{}  & New \Comment{&
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=188930}{\#188930}}}
    & - & \hi{} & Test262\\
   \bottomrule
  \end{tabular}
\end{table}
